---
title: "02 - R Programming - Week 2 - Assignment"
author: "Deborah"
date: "April 9, 2020"
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 2
editor_options:
  chunk_output_type: console
---

#Set Working Directory
```{r}
specdata <- ("D:/Data Science/Coursera/Data Science Specialization/R Programming Assignment/Week 2 Assignment/specdata/")
```

#Part 1 - Write Function for Pollutant Mean
```{r}
source("pollutantmean.R")
pollutantmean(specdata, "sulfate", 1:10)
pollutantmean(specdata, "nitrate", 70:72)
pollutantmean(specdata, "nitrate", 23)
```


#Part 2 - Write a Function that Uses the Directory and Reports the Number of Completely Observed Cases
```{r}
source("complete.R")
complete(specdata, 1)
complete(specdata, c(2, 4, 8, 10, 12))
complete(specdata, 30:25)
complete(specdata, 3)
```


#Part 3 - Write a Function that Takes the Directory and a Threshold for Complete Cases and Calculates the Correlation Between Sulfate and Nitrate for Monitor Locations Where the Number of Completely Observed Cases is Greater than the Threshold
```{r}
source("corr.R")
source("complete.R")
cr <- corr("specdata", 150)
head(cr)
summary(cr)

cr <- corr("specdata", 400)
head(cr)
summary(cr)

cr <- corr("specdata", 5000)
summary(cr)
length(cr)

cr <- corr("specdata")
summary(cr)
length(cr)
```